¿Qué pueden hacer las escuelas para disminuir la desigualdad en el conocimiento cívico?

### 2020-07-31 paper.Rmd
s

---
title: "¿Qué pueden hacer las escuelas para disminuir la desigualdad en el conocimiento cívico?"
author: "Yanara Jerez, Adonai Arancibia, Anais Herrera, Francisco Meneses y Victor Jimenez"
date: "31 de julio de 2020"
output: 
  html_document:
     theme: flatly
     highlight: tango
     toc: true
     toc_float: true
     toc_depth: 2
     number_sections: false
     code_folding: show
bibliography: "input/bib/Mi_biblioteca.bib"
cls: "input/bib/apa6.cls""
linkcolor: blue
link-citations: yes
---

>>>>

---
title: "¿Qué pueden hacer las escuelas para disminuir la desigualdad en el conocimiento cívico?"
author: "Yanara Jerez, Adonai Arancibia, Anais Herrera, Francisco Meneses y Victor Jimenez"
date: "31 de julio de 2020"
output: 
  html_document:
     theme: flatly
     highlight: tango
     toc: true
     toc_float: true
     toc_depth: 2
     number_sections: false
     code_folding: show
bibliography: 
  - input/bib/Mi_biblioteca.bib
cls: input/bib/apa6.cls
linkcolor: blue
link-citations: yes
---
